Reproducibility in Plant Pathology

### 2023-03-04 README.rmd
Add DOI for article and prep for v1.0.0 release
Fix DOI on Zenodo to point at all, not first release & increment version number

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (YYYY). _Openness and computational reproducibility in plant pathology: where do we stand and a way forward_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (2022). _Openness and computational reproducibility in plant pathology: where do we stand and a way forward_. agriRxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31220/agriRxiv.2021.00082>

@@

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

>>>>

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (2023). _Openness and computational reproducibility in plant pathology: where do we stand and a way forward_, _Phytopathology_ <https://doi.org/10.1094/PHYTO-10-21-0430-PER>.

@@

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (2023). _Openness and computational reproducibility in plant pathology: where do we stand and a way forward_. agriRxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31220/agriRxiv.2021.00082>

@@

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250664>
